\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
% Removed titlesec package - using custom section formatting instead

% Custom section formatting without titlesec
\renewcommand{\section}[1]{%
  \vspace{12pt}%
  {\Large\bfseries\MakeUppercase{#1}}%
  \vspace{2pt}%
  \hrule%
  \vspace{8pt}%
}
\newcommand{\entry}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill #4 \\
}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Tim Richardson}} \\
    \vspace{5pt}
    London, United Kingdom \\
    07828134100 \ \textbullet \ \href{mailto:tim@rewire.it}{tim@rewire.it} \\
    \href{http://rewire.it}{http://rewire.it} \ \textbullet \ \href{https://github.com/timini}{github.com/timini}
\end{center}

% --- SKILLS ---
\section{Technical Skills}
\textbf{Languages \& Tools:} node.js, django, elasticsearch, postgresql, docker, bioinformatics, reactjs, javascript, d3.js, python, scipy, numpy, git, amazon-web-services, kubernetes, graphql, google-cloud-platform, samtools, continuous-integration, continuous-deployment, tdd, microservices, unit-testing, web-services. \\
\textit{(Dislikes: php, perl)}

% --- EXPERIENCE ---
\section{Experience}

\entry{Genomics England}{London, UK}{Senior Software Engineer and Performance Development Lead}{Dec 2021 -- Present}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{Engineering Leadership:} Line Manager for 6 direct reports, responsible for mentorship, performance management, and delivery oversight.
    \item \textbf{Workflow Modernisation:} Key role in migrating complex workflow orchestration systems to Nextflow, improving scalability and reproducibility.
    \item \textbf{AI Transformation:} Leading internal initiative to introduce and operationalize AI coding assistants across engineering, driving efficiency.
    \item \textbf{Backend Development:} Architecting and maintaining robust backend services using Python and AWS for high-throughput genomic data processing.
\end{itemize}
\vspace{8pt}

\entry{IQVIA}{London, UK}{Senior Software Engineer - AI/ML Team}{Mar 2019 -- Dec 2021}
\textit{Stack: go, fastapi, typescript, reactjs, redux, elasticsearch, postgresql, d3.js}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{Full-Stack Development:} Built data analytics product for real-world healthcare data, developing backend services in Go and frontend in React.
    \item \textbf{AI Model Deployment:} Deployed machine learning models using FastAPI, enabling scalable inference for healthcare analytics.
    \item \textbf{Statistical Features:} Developed and implemented statistical features for the analytics product, enhancing data insights capabilities.
    \item Coordinating releases, product development, process improvement, code review.
\end{itemize}
\vspace{8pt}

\entry{Project Shivom}{London, UK}{Lead Developer}{Oct 2018 -- Mar 2019}
\textit{Stack: blockchain, smartcontracts, google-genomics, google-cloud-build, postgresql, graphql, react-apollo}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Design, development, and deployment of a genomic data sharing solution with blockchain components.
    \item Managed development team, created wireframes, developed backend services (REST APIs) and React SPA frontend.
    \item Deployed using Docker and App Engine.
\end{itemize}
\vspace{8pt}

\entry{Polecat}{London, UK}{Python Contractor}{Jul 2018 -- Oct 2018}
\textit{Stack: django, django-rest-framework, graphene-python, reactjs, elasticsearch, postgresql, plotly}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Built a Python reporting service to generate PowerPoint marketing reports.
    \item Engaged with technical teams and product managers to produce software specifications and wireframes.
    \item Solution built using Python, Django, GraphQL, React, Elasticsearch, and Plotly.js.
\end{itemize}
\vspace{8pt}

\entry{Congenica}{Hinxton, UK}{Senior Frontend Developer (React)}{Mar 2016 -- Jul 2018}
\textit{Stack: perl, reactjs, react-router, redux, reactive-programming, bioperl}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed new and optimised existing features for clinical genomics tool using Perl APIs and React frontend.
    \item Focused on optimal data flow for data-intensive UI.
    \item Led development of an API to integrate Congenica's Sapientia platform with Genomics England's 100k genomes project.
\end{itemize}
\vspace{8pt}

\entry{Repositive Ltd}{London, UK}{Lead Developer}{Nov 2014 -- Mar 2016}
\textit{Stack: docker, node.js, ansible, ember.js, git, agile, postgresql, elasticsearch}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Led development of a genomic data discovery platform, including infrastructure and development processes.
    \item Developed web app architecture based on Node.js Express API using Redis, Postgres, and Elasticsearch.
    \item Built UI as an Ember.js single-page application.
\end{itemize}
\vspace{8pt}

\entry{Wolfson Institute for Biomedical Research}{London, UK}{Freelance Bioinformatics Project}{Oct 2014 -- Nov 2014}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Analyzed ChIP-SEQ project: trimming and QC, peak calling, motif discovery, GO annotation.
\end{itemize}
\vspace{8pt}

\entry{Fire Tech Camp}{London, UK}{Instructor}{Jun 2014 -- Aug 2014}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Taught Python programming to children aged 11-15.
\end{itemize}
\vspace{8pt}

\entry{Ixxy}{Brighton/Remote}{Django Developer}{Mar 2013 -- May 2014}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Built and maintained sites based on Django/Python CMS system.
\end{itemize}
\vspace{8pt}

\entry{Ecomarket.com}{London, UK}{Django Developer}{Jan 2013 -- Mar 2013}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Backend developer for an online marketplace using Django, Python, and PostgreSQL.
\end{itemize}
\vspace{8pt}

\entry{Swerve Concepts}{London, UK}{Junior Software Developer}{Feb 2011 -- Jan 2013}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Full stack developer using Python and PHP frameworks. Developed cloud-based products Swerve Media Hub and SignUpAnywhere.
\end{itemize}

% --- EDUCATION ---
\section{Education}

\entry{Birkbeck, University of London}{London, UK}{MSc Bioinformatics \& Systems Biology (Merit)}{Sep 2012 -- Sep 2014}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Studied statistics, protein structure, sequence alignment, systems biology, and software development.
    \item Thesis: Tracing human migration using MCMC methods for population clustering with dense genotype data.
\end{itemize}
\vspace{8pt}

\entry{Leeds University}{Leeds, UK}{BSc Cognitive Science (Hons)}{Sep 2005 -- Sep 2008}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Interdisciplinary course covering computing, psychology, and philosophy.
    \item Dissertation: Data mining techniques for dynamic data sets.
\end{itemize}

% --- PROJECTS & INTERESTS ---
\section{Projects \& Interests}

\textbf{hansard} (\href{https://github.com/timini/hansard}{github.com/timini/hansard}) \\
Analysis of the hansard archive materials. Uses Jupyter, Django REST, Ember.js, Docker, Kubernetes.

\textbf{chromo9} (\href{https://github.com/timini/chromo9}{github.com/timini/chromo9}) \\
Biocomputing II project using Perl.

\textbf{keyzen} (\href{https://github.com/timini/keyzen}{github.com/timini/keyzen}) \\
A touch typing trainer geared towards programmers.

\end{document}